### 2020-08-15 thesis/appendix_2.tex
update appendix 2

%TODO Add description of each elements in this

>>>>

This appendix contains documents relevant to the stakeholder workshop of Chapter 2: 
\begin{itemize}
  \item \textbf{Feuille de route du Participant - Workshop participant roadmap} - This is the document that was given to each participant during the workshop. It contains helpful information meant to guide them during the exercises: the agenda for the day, a few illustrations of simple connectivity concepts, and suggestions of assets and obstacles to connectivity.
  \item \textbf{Document du facilitateur - Facilitator's sheet} - This is the document that was given to each facilitator. It contains guidelines for leading the conversation at each table and at each step of the workshop.
  \item \textbf{Certificate of Ethical Acceptability of Research Involving Humans} - This document certifies that this research project was approved by McGill's university Research Ethics Board Office.
\end{itemize}
